% !TEX program = lualatex
% chktex-file 26

\documentclass{article}
\usepackage[letterpaper,left=1.5cm,right=1.5cm,top=1.4cm,bottom=1.4cm]{geometry}
\usepackage[fontsize=9pt]{fontsize}
\usepackage{lmodern}

\pagestyle{empty} % remove page number
\linespread{1.25}
\hyphenpenalty=900
\righthyphenmin=3
\emergencystretch=1.5em

%====== LIST ======
\usepackage{enumitem}
\setlist[itemize]{left=1.2em}
% \setlist{noitemsep,nosep}

%====== LINKS AND METADATA ======
\usepackage[bookmarks=false]{hyperref}
\hypersetup{
  hidelinks,
  pdfpagemode=UseNone,
  pdftitle={Luis Urrutia Resume},
  pdfauthor={Luis Urrutia},
  pdfsubject={Curriculum Vitae},
  pdfkeywords={Software Engineer, React, React.js, TypeScript, JavaScript, Go, Next.js, Node.js}
}

\usepackage{microtype} % With hyphenation disabled, provide better spacing

%====== FONTS ======
\usepackage{fontspec}
\setmainfont{SourceSans3}[
   Path           = ./fonts/SourceSans3/,
   Ligatures      = TeX,
   Extension      = .ttf,
   UprightFont    = SourceSans3-Light.ttf,
   BoldItalicFont = SourceSans3-Italic.ttf,
   BoldFont       = SourceSans3-Regular.ttf,
   ItalicFont     = SourceSans3-ExtraLightItalic.ttf
]
\newfontfamily\Title{SourceSans3Title}[
   Path          = ./fonts/SourceSans3/,
   Extension     = .ttf,
   Ligatures     = TeX,
   UprightFont   = SourceSans3-Light.ttf,
   BoldFont      = SourceSans3-Medium.ttf,
]
\newfontfamily\SubSection{SourceSans3Title}[
   Path          = ./fonts/SourceSans3/,
   Extension     = .ttf,
   Ligatures     = TeX,
   UprightFont   = SourceSans3-Medium.ttf,
]

%====== TITLE FORMATTING ======
\usepackage{titlesec}
\titleformat{\section}{\Title\fontsize{10}{12}}{\thesection}{1em}{}[\titlerule]
\titleformat{\subsection}{\SubSection\fontsize{12}{10}}{\thesubsection}{1em}{}[]

%====== CUSTOM COMMANDS ======
\newcommand{\SubHeading}[1]{
   \subsection*{#1}\vspace{-0.5em}
}
\newcommand{\WorkExperience}[2]{
   \subsection*{#1}
   \vspace{-1em}
   \uppercase{#2}
}
\newcommand{\Skills}[1]{
   \textit{\textbf{Skills:} #1}
}

\input{content/shared-data.tex}

\begin{document}
\begin{center}
	\begin{minipage}{0.5\textwidth}
		{\fontsize{24}{28}\Title\addfontfeature{LetterSpace=5}{{\bfseries \ResumeNameFirst} \ResumeNameLast}} \\
		\bigskip
		{\normalsize \MakeUppercase{Senior Full-Stack Engineer}}
	\end{minipage} \hfill
	\begin{minipage}{0.4\textwidth}
		\raggedleft{}
		Email: \href{mailto:\ResumeEmail}{\ResumeEmail} \\
		Mobile: \href{tel:+34644402855}{+34 644 402 855}  \\
		Location: Madrid, Spain (EU) \\
		LinkedIn: \href{\ResumeLinkedInUrl}{\ResumeLinkedInLabel} \\
		GitHub: \href{\ResumeGitHubUrl}{\ResumeGitHubLabel}
	\end{minipage}
\end{center}

\vspace{-3em}

\phantom{Amazon, Microsoft, Facebook} % A/B Test

\section*{EXPERIENCE}
\WorkExperience{SOFTWARE ENGINEER \hfill UK, Remote}{OpenZeppelin \hfill 2023 {-} 2026} \\
\Skills{TypeScript, React, Next.js, Express.js, gRPC, Jest, Playwright, Cypress, GitHub Actions, AWS, AWS Lambda, Amazon SQS, DynamoDB, PostgreSQL, Redis, Docker, Kubernetes, Terraform, CloudWatch, Sentry, Stripe, Tailwind CSS, Svelte, Rust, Solidity}
\begin{itemize}
\item Co-led Defender 2.0 Secure Audit as one of two engineers, delivering a TypeScript and React module for auditors and clients with a Next.js architecture that balanced SSR and SPA needs.
\item Built SDK capabilities for Defender and open-source Relayer so developers could integrate product workflows, including integration paths that relied on gRPC interfaces.
\item Built Stripe billing integration in Defender 2.0 for self-serve Pro subscriptions and enterprise-tier plans.
\item Led end-to-end testing for Defender with Playwright, focusing on critical user flows to improve release confidence.
\item Refactored the TypeScript monorepo build system and reduced build times from about 15 minutes to 3 minutes in local and CI runs while reducing bundle size.
\item Owned the EVM side of the Rust-based OpenZeppelin Relayer OSS work, including RPC balancing, retry and failover, AWS KMS and GCP KMS signer integrations, and a fix for a critical nonce race condition.
\end{itemize}

\WorkExperience{SOFTWARE ENGINEER \hfill US, Remote}{Premise \hfill 2021 {-} 2022} \\
\Skills{React, TypeScript, JavaScript, Next.js, Express.js, Protocol Buffers, Apollo GraphQL, GraphQL, Jest, GitHub Actions, Material-UI, Storybook, Tailwind CSS, PostgreSQL, BigQuery, GCP, Kubernetes, Docker, Python}
\begin{itemize}
\item Built a presentation-sharing feature in MyPremise with React and TypeScript so account managers and clients could share live links instead of static screenshots in PDF or PPT files.
\item Used Next.js server-side rendering patterns for user-facing views where pre-rendered responses improved delivery for shared reporting pages.
\item Contributed to the migration from REST to GraphQL with Apollo across key entities, including updates to Express.js services, improving API response times by 35\% and lowering server usage.
\item Worked on API integration contracts that included Protocol Buffers in backend communication workflows.
\item Improved release reliability by expanding test coverage with Jest and adding quality gates in GitHub Actions, reducing release cycles from one week to less than 24 hours.
\item Helped standardize the UI with Material UI and introduced Storybook for shared component documentation and design handoff, reducing prototyping time from one week to one day.
\end{itemize}

\WorkExperience{SYSTEM ARCHITECT \hfill Santiago, Chile}{Vitamina Holding \hfill 2019 {-} 2022} \\
\Skills{TypeScript, React, JavaScript, Express.js, Node.js, Tailwind CSS, Git, MySQL, Amazon Web Services (AWS), Azure, Kubernetes, Docker, Angular, Python, C\#}
\begin{itemize}
\item Improved architecture and delivery process for a legacy internal platform built on .NET Framework and Microsoft tooling.
\item Worked with product, engineering, and infrastructure teams to simplify release flow and reduce delivery cycles from months to about two weeks.
\item Implemented transaction-related API flows with Express.js, including integrations with Transbank for payment processing use cases.
\item Introduced DevOps practices and led a staged migration from on-prem to Azure hybrid infrastructure across applications, databases, jobs, storage, and networking.
\end{itemize}

\WorkExperience{SOFTWARE ENGINEER \hfill Colombia, Remote}{Rappi \hfill 2020 {-} 2021} \\
\Skills{Go, TypeScript, JavaScript, Node.js, Angular, Python, Kafka, Redis, PostgreSQL, Amazon Web Services (AWS), Docker, Kubernetes, Git}
\begin{itemize}
\item Built backend integrations for merchant ingestion pipelines, normalizing data from FTP, APIs, SOAP XML feeds, and web scraping to support pricing, stock, availability, bundles, and product attributes.
\item Built an internal onboarding platform with Go and Angular that replaced manual YAML and TOML configuration managed by an external engineering team, saving \$75,000 annually.
\item Implemented event-driven catalog and pricing updates with Go and Kafka so product and discount changes reached the app faster and contributed to a 21\% increase in CSAT.
\item Added a Redis-based conflict resolution layer for duplicate events, out-of-order updates, stale writes, and pricing inconsistencies, improving product data accuracy and reliability by 40\%.
\item Increased unit test coverage for critical pricing and discount logic, reducing critical rollout defects by 33\% and improving release confidence.
\end{itemize}

\WorkExperience{FULL STACK DEVELOPER \hfill Santiago, Chile}{Resit SPA \hfill 2017 {-} 2019} \\
\Skills{TypeScript, React, Redux, JavaScript, Express.js, React Native, Tailwind CSS, GraphQL, Angular, Django, Python, MySQL, Amazon Web Services (AWS), Docker, Kubernetes, Git}
\begin{itemize}
\item Delivered more than five web and mobile products for clients across medical, industrial, government, legal, and cultural sectors, working end to end from discovery and requirements to planning and implementation.
\item Led architecture decisions for each project and set engineering standards for TypeScript, React, and React Native across the company.
\item Implemented predictable frontend state management patterns with Redux on client-facing React products.
\item Implemented payment gateway integrations with Express.js services, including Transbank transaction flows for client projects.
\item Mentored five developers through pairing sessions, code reviews, and workshops focused on architecture, testing, and code quality.
\end{itemize}

\WorkExperience{FULLSTACK DEVELOPER \hfill Santiago, Chile}{Dxpress \hfill 2015 {-} 2017} \\
\Skills{Go, TypeScript, JavaScript, Flask, Python, Angular, PostgreSQL, Redis, Tile38, Google Cloud Platform (GCP), Git}
\begin{itemize}
\item Helped build Dxpress from idea to launch as one of the first Uber Eats-style delivery platforms in Chile, collaborating with a small team on product and technical decisions.
\item Built backend services with Flask and Python, and later Go, for search, notifications, and geolocation using Tile38 across consumer, merchant, courier, and internal administration applications.
\item Developed cron-based ETL pipelines that ingested and normalized product data from manual uploads, APIs, web scraping, and FTP CSV files, supporting catalogs with more than 5,000 products.
\item Built operational dashboards for fulfillment rate, order volume, and delivery time, helping the team adjust courier allocation quickly as conditions changed.
\end{itemize}

\WorkExperience{JUNIOR SOFTWARE DEVELOPER \hfill Santiago, Chile}{Laboratorio de Ideas Ltda. \hfill 2015 {-} 2015} \\
\Skills{JavaScript, Node.js, AngularJS, Django, Python, Laravel, PHP, Vagrant}

\section*{EDUCATION}
\SubHeading{Bachelor of Engineering in Computer Science \hfill Santiago, Chile}
Universidad Tecnologica de Chile \\[0.1em]
2012 {-} 2015

\section*{SKILLS}
\begin{itemize}
	\item \textbf{Frontend \& UI:} React, Next.js, React Native, Tailwind CSS, Storybook, Material-UI, Svelte, Angular, AngularJS, HTML5, CSS
	\item \textbf{Languages:} TypeScript, JavaScript, C\#, Rust, Python, Go, Solidity, PHP
	\item \textbf{Testing \& QA:} Playwright, React Testing Library, Jest, Cypress, Pytest
	\item \textbf{Backend \& APIs:} Node.js, Express.js, GraphQL, REST APIs, WebSockets
	\item \textbf{Databases \& Messaging:} PostgreSQL, MySQL, Redis, DynamoDB, BigQuery, Kafka, Amazon SQS, Tile38
	\item \textbf{Cloud \& DevOps:} AWS, AWS Lambda, GCP, Azure, Docker, Kubernetes, Terraform, GitHub Actions, CloudWatch, Serverless
	\item \textbf{Platforms \& Practices:} Stripe, Agile, Scrum, Git, CI/CD, Microservices
\end{itemize}

\section*{LANGUAGES}
\begin{itemize}[left=0pt]
	\item \textbf{SPANISH}: Native
	\item \textbf{ENGLISH}: Advanced {-} C1
\end{itemize}

\end{document}

