% !TEX program = lualatex
% chktex-file 26

\documentclass{article}
\usepackage[letterpaper,left=1.5cm,right=1.5cm,top=1.4cm,bottom=1.4cm]{geometry}
\usepackage[fontsize=9pt]{fontsize}
\usepackage{lmodern}

\pagestyle{empty} % remove page number
\linespread{1.25}
\hyphenpenalty=900
\righthyphenmin=3
\emergencystretch=1.5em

%====== LIST ======
\usepackage{enumitem}
\setlist[itemize]{left=1.2em, itemsep=0.2em, topsep=0.3em, parsep=0pt, partopsep=0pt}
% \setlist{noitemsep,nosep}

%====== LINKS AND METADATA ======
\usepackage[bookmarks=false]{hyperref}
\hypersetup{
  hidelinks,
  pdfpagemode=UseNone,
  pdftitle={Luis Urrutia Resume},
  pdfauthor={Luis Urrutia},
  pdfsubject={Curriculum Vitae},
  pdfkeywords={Software Engineer, React, React.js, TypeScript, JavaScript, Go, Next.js, Node.js}
}

\usepackage{microtype} % With hyphenation disabled, provide better spacing

%====== FONTS ======
\usepackage{fontspec}
\setmainfont{SourceSans3}[
   Path           = ./fonts/SourceSans3/,
   Ligatures      = TeX,
   Extension      = .ttf,
   UprightFont    = SourceSans3-Light.ttf,
   BoldItalicFont = SourceSans3-Italic.ttf,
   BoldFont       = SourceSans3-Regular.ttf,
   ItalicFont     = SourceSans3-ExtraLightItalic.ttf
]
\newfontfamily\Title{SourceSans3Title}[
   Path          = ./fonts/SourceSans3/,
   Extension     = .ttf,
   Ligatures     = TeX,
   UprightFont   = SourceSans3-Light.ttf,
   BoldFont      = SourceSans3-Medium.ttf,
]
\newfontfamily\SubSection{SourceSans3Title}[
   Path          = ./fonts/SourceSans3/,
   Extension     = .ttf,
   Ligatures     = TeX,
   UprightFont   = SourceSans3-Medium.ttf,
]

%====== TITLE FORMATTING ======
\usepackage{titlesec}
\titleformat{\section}{\Title\fontsize{10}{12}}{\thesection}{1em}{}[\titlerule]
\titleformat{\subsection}{\SubSection\fontsize{12}{10}}{\thesubsection}{1em}{}[]

%====== CUSTOM COMMANDS ======
\newcommand{\SubHeading}[1]{
   \subsection*{#1}\vspace{-0.5em}
}
\newcommand{\WorkExperience}[2]{
   \subsection*{#1}
   \vspace{-1em}
   \uppercase{#2}
}
\newcommand{\Skills}[1]{
   \textit{\textbf{Skills:} #1}
}

\input{content/shared-data.tex}

\begin{document}
\begin{center}
	\begin{minipage}{0.5\textwidth}
		{\fontsize{24}{28}\Title\addfontfeature{LetterSpace=5}{{\bfseries \ResumeNameFirst} \ResumeNameLast}} \\
		\bigskip
		{\normalsize \MakeUppercase{Senior Full-Stack Engineer}}
	\end{minipage} \hfill
	\begin{minipage}{0.4\textwidth}
		\raggedleft{}
		Email: \href{mailto:\ResumeEmail}{\ResumeEmail} \\
		Mobile: \href{tel:+34644402855}{+34 644 402 855}  \\
		Location: Madrid, Spain (EU) \\
		LinkedIn: \href{\ResumeLinkedInUrl}{\ResumeLinkedInLabel} \\
		GitHub: \href{\ResumeGitHubUrl}{\ResumeGitHubLabel}
	\end{minipage}
\end{center}

\vspace{-3em}

\phantom{Amazon, Microsoft, Facebook} % A/B Test

\section*{EXPERIENCE}
\WorkExperience{SOFTWARE ENGINEER \hfill UK, Remote}{OpenZeppelin \hfill 2023 {-} 2026} \\
\Skills{React, TypeScript, Next.js, Zustand, Rust, Solidity, AWS, Kubernetes, Terraform, Docker, PostgreSQL, Redis, Playwright}
\begin{itemize}
\item Co-led OpenZeppelin Defender 2.0 Secure Audit as one of two engineers, building a \textbf{React and TypeScript module} with Zustand so auditors could work with clients, track findings, verify fixes, and deliver final PDF reports.
\item Owned the EVM side of the Rust-based open-source Relayer, including \textbf{RPC balancing and failover}, cloud KMS signer integrations, chain-specific transaction cost handling, and a fix for a critical nonce race condition.
\item Built \textbf{SDK capabilities for developers} across Defender and the open-source Relayer so technical teams could integrate the products and create custom automation tooling.
\item Shaped \textbf{frontend architecture decisions} for OIF and Ascend across rendering strategy, state management, i18n, Kubernetes, and Okta.
\item Led \textbf{critical user-flow testing} for Defender with Playwright to improve release confidence.
\item Refactored the TypeScript monorepo build system, reducing local and CI build times from about \textbf{15 minutes to 3 minutes} while reducing bundle size and speeding up PR cycles.
\end{itemize}

\WorkExperience{SOFTWARE ENGINEER \hfill US, Remote}{Premise \hfill 2021 {-} 2022} \\
\Skills{React, TypeScript, Next.js, GraphQL, Apollo GraphQL, Storybook, Material-UI, GCP, Kubernetes, Docker, PostgreSQL, Jest}
\begin{itemize}
\item Built a \textbf{live-data presentation feature} in React and TypeScript so account managers and clients could use a single shareable URL instead of resending PDF or PPT exports.
\item Contributed to the \textbf{REST to GraphQL migration} with Apollo across key entities, improving API response times by 35\% and lowering server usage.
\item Helped standardize the UI with \textbf{Material UI and Storybook} for shared component documentation and design handoff, reducing prototyping time from one week to one day.
\item Improved \textbf{release reliability} by expanding Jest coverage and adding quality gates, reducing release cycles from one week to less than 24 hours.
\item Built an internal hackathon AI proof of concept using the OpenAI API for natural-language report generation.
\end{itemize}

\WorkExperience{SYSTEM ARCHITECT \hfill Santiago, Chile}{Vitamina Holding \hfill 2019 {-} 2022} \\
\Skills{React, TypeScript, Redux, Express.js, Python, AWS, Azure, Kubernetes, Docker, MSSQL, MySQL, C\#}
\begin{itemize}
\item Improved \textbf{architecture and delivery} for a legacy internal platform, working with product, engineering, and infrastructure teams to reduce delivery cycles from months to about two weeks.
\item Modernized key parts of the stack by moving from ASP.NET to Angular and from .NET Framework to .NET Core, removing Internet Explorer-only constraints and enabling Chrome compatibility.
\item Implemented transaction-related API flows with Express.js, including integrations with Transbank for payment processing use cases.
\item Led a staged \textbf{Azure hybrid migration} across applications, databases, jobs, storage, and networking.
\end{itemize}

\WorkExperience{SOFTWARE ENGINEER \hfill Colombia, Remote}{Rappi \hfill 2020 {-} 2021} \\
\Skills{Go, Kafka, Redis, PostgreSQL, TypeScript, Python, AWS, Kubernetes, Docker, Angular}
\begin{itemize}
\item Implemented \textbf{real-time catalog and pricing} updates with Go and Kafka, moving core logic from a Python ETL flow and contributing to a 21\% CSAT increase.
\item Engineered a \textbf{Redis conflict-resolution layer} that prioritized real-time event processing over scheduled tasks and improved product data reliability by 40\%.
\item Led an \textbf{internal onboarding platform} with Go, Node.js, and Angular, saving \$75,000 annually and enabling faster customer-service onboarding.
\item Built \textbf{merchant ingestion pipelines} from FTP, APIs, SOAP XML feeds, and web scraping for pricing, stock, availability, bundles, and product attributes.
\item Drove unit testing for critical pricing, offers, and bundles logic with an 80\% coverage target, reducing critical rollout defects by 33\%.
\end{itemize}

\WorkExperience{FULL STACK DEVELOPER \hfill Santiago, Chile}{Resit SPA \hfill 2017 {-} 2019} \\
\Skills{React, TypeScript, React Native, Redux, GraphQL, Express.js, Python, Django, AWS, Kubernetes, Docker, MongoDB, MySQL}
\begin{itemize}
\item Delivered \textbf{five-plus client products} across medical, industrial, government, legal, and cultural sectors, working from discovery and requirements through planning and implementation.
\item Led \textbf{architecture and engineering standards} for TypeScript, React, React Native, and Redux across the company.
\item Built React Native mobile applications for client products, aligning app architecture and delivery practices with shared web platform standards.
\item Mentored five developers through pairing sessions, code reviews, and workshops focused on architecture, testing, and code quality.
\item Worked directly with clients through discovery calls, demos, and status updates, including a short-deadline government project that helped open agency opportunities.
\end{itemize}

\WorkExperience{FULLSTACK DEVELOPER \hfill Santiago, Chile}{Dxpress \hfill 2015 {-} 2017} \\
\Skills{Go, Python, Redis, PostgreSQL, GCP, Flask, Angular, Tile38}
\begin{itemize}
\item Contributed to building Dxpress from idea to launch as one of Chile's first \textbf{Uber Eats-style delivery services} inside a small product and engineering team.
\item Built backend capabilities across Python and Go for \textbf{geolocation and real-time operations}, advanced search, and product ETL workflows.
\item Developed ETL pipelines that ingested and normalized product data from manual uploads, APIs, web scraping, and FTP CSV files, supporting catalogs with more than 5,000 products.
\end{itemize}

\WorkExperience{JUNIOR SOFTWARE DEVELOPER \hfill Santiago, Chile}{Laboratorio de Ideas Ltda. \hfill 2015 {-} 2015} \\
\Skills{AngularJS, JavaScript, Node.js, Python, Django}
\begin{itemize}
\item Started as a junior developer and took on growing frontend ownership, helping introduce Node.js and AngularJS into the agency stack.
\end{itemize}

\section*{EDUCATION}
\SubHeading{Bachelor of Engineering in Computer Science \hfill Santiago, Chile}
Universidad Tecnologica de Chile \\[0.1em]
2012 {-} 2015

\section*{SKILLS}
\begin{itemize}
	\item \textbf{Frontend \& UI:} React, Next.js, Zustand, Redux, React Native, Storybook, Material-UI
	\item \textbf{Languages:} TypeScript, Go, Rust, Python, Solidity, JavaScript
	\item \textbf{Backend \& APIs:} WebSockets, REST APIs, GraphQL, Apollo GraphQL, Node.js, Express.js
	\item \textbf{Databases \& Messaging:} Redis, Kafka, PostgreSQL, DynamoDB, MySQL, BigQuery
	\item \textbf{Cloud \& DevOps:} AWS, GCP, Azure, Kubernetes, Docker, Terraform, CI/CD
	\item \textbf{Testing \& QA:} Playwright, Jest, Cypress, React Testing Library, Pytest
\end{itemize}

\section*{LANGUAGES}
\begin{itemize}[left=0pt]
	\item \textbf{Spanish language}: Native
	\item \textbf{English language}: Advanced {-} C1
\end{itemize}

\end{document}
